Big Brother Is Watching

### 2015-11-05 manuscript.tex
Some git bs

\section{Abstract}
\label{sec:abstract}
Several models were developed to facilitate the perpetual surveillance of Gotham City using . These models account

\section{General Assumptions}
\label{sec:general_assumptions}
\paragraph{Representing Manhattan}
\label{par:representing_manhattan}
First, we want to justify our representation of Manhattan. Manhattan is a long thin strip of land, spanned vertically by \emph{avenues} and horizontally by \emph{streets}. Manhattan is effectively 250 streets long, and 10 avenues wide. A Manhattan city block is \SI{80}\m by \SI{274}\m. We can approximate Manhattan, or at least this hypothetical version of Manhattan as part of Gotham City, to be a grid 250 blocks long by 30 blocks wide, where a block is an arbitrary unit of distance, in this case \SI{80}\m. In this representation, Central Park is 10 blocks wide and 51 blocks long, since the real Central Park is 3 avenues wide and goes from \nth{59} Street to \nth{110} Street, occupying the middle 3 avenues \cite{centralpark}. Similarly, if we take Gotham University to be the fictional equivalent of Columbia University, which is found between \nth{110} Street and \nth{122} Street and spans the 3 westernmost avenues of Manhattan \cite{columbia}, then we can it to be an area 12 block long and 9 blocks wide. Finally, the Financial District is contained in the southernmost 20 streets in Manhattan \cite{financial}, hence we can make it occupy the last 20 rows in our matrix.

@@

% Nimit's stuff and things
\section{Block Model}
\label{sec:block_model}
The block model assumes that an approximation to the optimal number of drones can be achieved by splitting up Manhattan into non-overlapping rectangular blocks, each of which is assigned a drone to cover that area. The rectangles must therefore be small enough so that the drones can cover them in 15 minutes. Our algorithm iterates through all pairs of rectangle dimensions that are small enough for a single drone to cover in 15 minutes, and tiles Manhattan with these rectangles. If the dimension of Manhattan is not divisible by the rectangle dimension, we take the "leftover" area that is not covered by any rectangle and pass that area back into a recursive call to the algorithm (it may be tiled with different-sized rectangles). Finally, we select the tiling arrangement that covers Manhattan with the least number of blocks, and therefore the fewest drones.

To do this, we first need to determine how long it takes for a single drone to survey a rectangular block of dimension m by n. However, we also note that for the drone to survey a collection of points every $x$ minutes, it is not enough to simply visit all of the points within $x$ minutes, it must also \textit{return to the starting point} within $x$ minutes, otherwise the starting point will go more than $x$ minutes without being visited.

To simplify things, select some time step such that the drone can survey exactly one grid point per time step. Then, if either $m$ or $n$ is even, the amount of time it takes is just $m*n$. Proof: See Figure \ref{path} in section 4, and note that the number of "zigzags" is even and the path does not cross over itself. However, if neither is even, we may not be able to traverse the rectangle and return to the starting position in $m*n$ steps. Instead, we can traverse the rectangle in a similar zigzag pattern (with the long edge of the zigzags perpendicular to the longer edge of the rectangle), and then at the end of the last zigzag (which will end in the middle of the rectangle instead of at the starting corner), move towards the starting corner, which will take $min(m,n) - 1$ time (see Figure \ref{path2}). The exception to both cases is if either $m$ or $n$ is 1. Assume WLOG that $m = 1$; in this case, it will take $2n - 1$ time to traverse all the grid points and return to the starting position, since once we traverse all the grid points (say, from "left to right"), which takes $n - 1$ steps, we will have to retrace our steps, which takes $n-1$ more steps.

\begin{figure}[htb!]
    \centering{{\includegraphics[width=7cm]{figures/odd_path.pdf} }}
    \caption{The shape of a path in a rectangle with an odd height and odd width. The path begins in the top right corner and goes to the left, and reverses directions from downward to upward when it gets to the bottom right corner.}
    \label{path2}
\end{figure}

Using this formula, we are ready to find the optimal arrangement of rectangular blocks that covers Manhattan while using the fewest drones.

For example, when we model Manhattan as a 30 by 250 grid, and if we assume that each drone can survey one grid point per minute, then the algorithm tells us that the "main" tiling will be 7 by 2 blocks. So, a contiguous 28 by 250 area (without loss of generality, we can assume it is in the upper left corner) will be covered with a 4 by 125 tiling of rectangular blocks. Then, there is a 2 by 250 area remaining. This area will be tiled with 35 2 by 7 blocks. Finally, there will be a 2 by 5 block left over. This block is small enough for one drone to survey in one minute. Therefore, the total number of blocks is $4*125 + 35 + 1 = 500 + 36 = 536$ blocks, and so 536 drones.

If we assume each drone can survey ten grid points per minute, then we get that the main tiling will be a 10 by 5 tiling of 3 by 50 blocks. There is no space left over (every grid point is covered by some block), so the total number of drones is just 50.

This method can be extended to the case where some areas must be observed more often than others. We can just assume that these areas are rectangular (which is a fairly good assumption in this case) and treat these areas as separate blocks.

@@

>>>>

\section{Abstract}
\label{sec:abstract}
Several models were developed to facilitate the perpetual surveillance of Gotham City using Micro unmanned Aerial Vehicles in order to catch jaywalkers. These models are optimized to handle separate scenarios involving maximum visit intervals, sharp turns requiring more energy/fuel, recharging/fueling rates, densities of jaywalkers, and the biased knowledge of the drone programmers. We represent Gotham City as rectangular grid in order to simplify our models. Our three approaches that handle these problems consist of an optimal path/contingency model that minimizes the number of turns and accounts for drone failures, a blocking model that subdivides Gotham in to smaller rectangles that individual drones traverse, and a greedy random walk model that adds a randomized effect to the drones paths. 
\section{General Assumptions}
\label{sec:general_assumptions}
\paragraph{Representing Manhattan}
\label{par:representing_manhattan}
First, we want to justify our representation of Manhattan. Manhattan is a long thin strip of land, spanned vertically by \emph{avenues} and horizontally by \emph{streets}. Manhattan is effectively 250 streets long, and 10 avenues wide. A Manhattan city block is \SI{80}\m by \SI{274}\m. We can approximate Manhattan, or at least this hypothetical version of Manhattan as part of Gotham City, to be a grid 250 blocks long by 30 blocks wide, where a block is an arbitrary unit of distance, in this case \SI{80}\m. In this representation, Central Park is 10 blocks wide and 51 blocks long, since the real Central Park is 3 avenues wide and goes from \nth{59} Street to \nth{110} Street, occupying the middle 3 avenues \cite{centralpark}. Similarly, if we take Gotham University to be the fictional equivalent of Columbia University, which is found between \nth{110} Street and \nth{122} Street and spans the 3 westernmost avenues of Manhattan \cite{columbia}, then we can it to be an area 12 block long and 9 blocks wide. Finally, the Financial District is contained in the southernmost 20 streets in Manhattan \cite{financial}, hence we can make it occupy the last 20 rows in our matrix.

@@

% Nimit's stuff and things
\section{Block Model}
\label{sec:block_model}

@@

\subsection{Contingency Source}
\label{sub:contingency_source}
\lstinputlisting{models/drone_failures.m}
